Statistical quantification of confounding bias in predictive modelling

### 2021-10-29 supplement.tex

@@

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.75\paperwidth]{fig/raw/sim_h1_ccc_partial_d10e0_sig_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'partial' confounder test, with normal conditional distribution and sigmoid dependence.}
  \label{fig:sim-ccc-sig-partial}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_bbb_partial_d10e0_lin_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'partial' confounder test, with categorical variables, normal conditional distribution and linear dependence.}
  \label{fig:sim-bbb-lin-partial}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_bbb_full_d1e0_linear_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'full' confounder test, with numerical variables, normal conditional distribution and linear dependence.}
  \label{fig:sim-ccc-lin-full}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_bbb_full_d1e0_linear_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'full' confounder test, with categorical variables, normal conditional distribution and linear dependence.}
  \label{fig:sim-bbb-lin-full}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_ccc_partial_d10e0_sig_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'partial' confounder test, with numerical variables, normal conditional distribution and sigmoid dependence.}
  \label{fig:sim-ccc-sig-partial}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_bbb_partial_d10e0_sig_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'partial' confounder test, with categorical variables, normal conditional distribution and sigmoid dependence.}
  \label{fig:sim-bbb-sig-partial}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_ccc_full_d1e0_sigmoid_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'full' confounder test, with numerical variables, normal conditional distribution and sigmoid dependence.}
  \label{fig:sim-ccc-sig-full}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.4\paperwidth]{fig/raw/sim_h1_bbb_full_d1e0_sigmoid_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'full' confounder test, with categorical variables, normal conditional distribution and sigmoid dependence.}
  \label{fig:sim-bbb-sig-full}
\end{figure}

@@
